Subject specific curves for time series forecasting of smart meter demand

### 2019-11-01 sscts-paper-1.Rmd
Anonymise data in main_df and move all preprocessing (except bad data filtering) before caching.

#### Parameters ===============================================================
# Data
data_dir <- "/mnt/Documents/data/building_level"
qh_path <- file.path(data_dir, "qh_2018")
outlier_file <- file.path(data_dir, "outlier_dates_20181120.csv")
attribute_file <- file.path(data_dir, "attributes_20181019_tidy.csv")
building_list_file <- file.path(data_dir, "building_list_20181022.csv")
all_data_file <- "cache/data_all_2018_sscts.RData"
fs_df_file <- "cache/fs_df.RData"
model_df_file <- "cache/model_df.RData"

@@

#### Setup ====================================================================
# Run if qh .RData file hasn't been created
if (!file.exists(all_data_file)) {
  cat("Processing data...\n\n")
  main_df <- load_all_data(
    attribute_file = attribute_file,
    qh_path = qh_path,
    building_list_file = building_list_file,
    business_days = TRUE
  )
  save(main_df, file = all_data_file)
} else {
  cat("Loaded cached processed data...\n\n")
  load(all_data_file)
}

@@

>>>>

#### Parameters ===============================================================
# Data
data_dir <- "/mnt/Documents/data/building_level"
qh_path <- file.path(data_dir, "qh_2018")
outlier_file <- file.path(data_dir, "outlier_dates_20181120.csv")
attribute_file <- file.path(data_dir, "attributes_20181019_tidy.csv")
building_list_file <- file.path(data_dir, "building_list_20181022.csv")
all_data_file <- "cache/main_df.RData"
fs_df_file <- "cache/fs_df.RData"
model_df_file <- "cache/model_df.RData"

@@

#### Setup ====================================================================
# Run if qh .RData file hasn't been created
if (!file.exists(all_data_file)) {
  cat("Processing data...\n\n")
  main_df <- load_all_data(
    attribute_file = attribute_file,
    qh_path = qh_path,
    building_list_file = building_list_file,
    business_days = TRUE
  )

@@

  save(main_df, file = all_data_file)
} else {
  cat("Loaded cached processed data...\n\n")
  load(all_data_file)
}
